Introductory statistics with `intRo`

### 2016-05-26 jcgs-paper-2016/response.Rmd

This is an intelligent paper describing interesting software, but it (and the associated software) suffer from three problems:

(1) The paper seems to me inappropriate for the JCGS. Because it focuses purely on software, I think that (once the other issues are addressed) it would be more appropriate for the Journal of Statistical Software or the R Journal.

(2) Although the software looks promising, unless I've missed something, it currently has very limited functionality -- indeed, not enough to sustain most introductory statistics courses. This isn't a permanent limitation, however, since the authors have created interesting infrastructure for extending the software. In its current state, the software doesn't quite look ready for prime time.

**Our intent was not for `intRo` to sustain an introductory statistics course, but rather to supplement it. In other words, limited functionality was actually a design goal from the beginning so as not to overwhelm a student seeing statistics for the first time. While we agree that it is likely there will be course topics that `intRo` doesn't support, if additional functionality is desired by the instructor, more modules can be added to support this.**

@@

R Commander should enter the discussion around here (even though it isn’t online)

P 5: Fig 2 shows a simple design that should be easy for casual users (as intro students really are) to get their heads around. Not all that keen on the use of “statistics” as a category heading in Panel 2 because it reinforces the ghettoizing of the word conflicting with a message that says everything you are doing here is statistics.

P 6 top: When you look at the actual R code generated it can be quite complex with its pipe structures etc which I would have thought does rather limit its introductory value.

**We appreciate the comment. In teaching R Workshops at Iowa State, we observed that among the majority of the introductory R students we encountered, the pipe structure was often preferred to using traditional nested function calls. TODO: modify this to show that pipe structure is used more frequently. The pipe structure is also the standard by which `ggvis` plots are created, which we are using as the backend to our graphical module. It would also be a relatively simple task for an instructor to modify or remove the piping structure in a modified version of `intRo` for use in a particular class.**

@@

P 6-7: discussion of particular modules should be in a “for example” vein. There is no need to justify what particular features are and are not included. (That would be in a teaching paper.)

**We have removed the in-depth discussion about the particular modules, and instead more vaguely described the functionality. We have also made sure to indicate that the full documentation is available online, which covers the supported functionality of every provided module.**

P 7 top: Being able to choose only plot types that are “compatible” with the variables used does, however, preclude learning experiences of the form “this thing you want to do is not appropriate for this type of data.”

**We have also gone back and forth on this issue. The reasoning behind choosing only plot types compatible is that the user will see the different plot types available as they select different variables. So while the teaching moment could take place post-selection (by, for instance, producing an error if a plot type is used with incompatible variable types), we chose to have the teaching moment be a step earlier, where the student may see the list and wonder why the plot type they thought they wanted is not actually an option. We felt that for a lot of introductory students, seeing a red error message is a frustrating moment and can discourage them from having any sort of autonomy within the software. Further, by doing a transformation of a variable, the plot types will automatically appear if they are compatible.**

### 2016-05-26 jcgs-paper-2016/paper.Rmd
More response updates

Although users can access intRo from \url{http://www.intro-stats.com}, course instructors may wish to download, customize, and their own instance, perhaps with new modules or modified theming or functionality. `intRo` can be downloaded, ran, and deployed on ShinyApps.io through the use of the R package `intRo`. Currently, the package is only available on GitHub, and can be installed using the devtools package as follows:

>>>>

Although users can access intRo from \url{http://www.intro-stats.com}, course instructors may wish to download, customize, and deploy their own instance, perhaps with new modules or modified theming or functionality. `intRo` can be downloaded, ran, and deployed on ShinyApps.io through the use of the R package `intRo`. Currently, the package is only available on GitHub, and can be installed using the devtools package as follows:
